---
title: "README"
author: "Me"
date: "April 30, 2017"
output: md_document
---

[![Travis-CI Build Status](https://travis-ci.org/Zelazny7/onehot.svg?branch=master)](https://travis-ci.org/Zelazny7/onehot)

```{r, echo=FALSE}
options(width=250)
```

## Onehot package

### Installation

```{r, eval=FALSE}
devtools::install_github("https://github.com/Zelazny7/onehot")
```

### Usage

```{r}
set.seed(100)
test <- data.frame(
  factor    = factor(sample(c(NA, letters[1:3]), 100, T), exclude=NULL),
  integer   = as.integer(runif(100) * 10),
  real      = rnorm(100),
  logical   = sample(c(T, F), 100, T),
  character = sample(letters, 100, T),
  stringsAsFactors = FALSE)

head(test)
```

### Create a onehot object

A onehot object contains information about the data.frame. This is used to 
transform a data.frame into a onehot encoded matrix. It should be saved to
transform future datasets into the same exact layout.

```{r}
library(onehot)
encoder <- onehot(test)

## printe a summary
encoder
```

### Transforming data.frames

The onehot object has a predict method which may be used to transform a
data.frame. Factors are onehot encoded. Character variables are skipped.
However calling predict with `stringsAsFactors=TRUE` will convert character
vectors to factors first.

```{r}
train_data <- predict(encoder, test)
head(train_data)
```

### NA indicator columns

`addNA=TRUE` will create an indicator column for every valid input column. This
is useful for algorithms that do not support missing values.

```{r}
#encoder <- onehot(test, addNA=TRUE)
#train_data <- predict(encoder, test)
#head(train_data)
```


### Sparse Matrices

`onehot` also provides support for predicting sparse, column compressed matrices
from the `Matrix` package:

```{r}
encoder <- onehot(test)
train_data <- predict(encoder, test, sparse=TRUE)
head(train_data)
```
